Automated Topic Naming

### 2012-01-20 ese/ese-major-response.tex

Within this new revision, we addressed this issue in a new section on inter-rater
reliability (5.3) and referenced this discussion in the threats to
validity (5.4) and the conclusion.

Furthermore, we expanded the discussion with statistical evidence that our IRR results were mostly
better than noise. We did extensive simulations sampling our ratings,
and then comparing those ratings against our ratings. We found that the
majority of our labels received higher IRR scores than 96\% to 99.9\%
of the random simulations. This allows us to confidently state that our
labels were primarily better than random. But we recognize that the
average of the values is low, and Section 5.3 address the threats this causes to
this paper, and what it might mean for practitioners and other
researchers when replicating this study. Section 5.3 also addresses the reviewers concerns that the IRR scores would
affect our ROC and F-Measure scores.

>>>>

We addressed this issue in a new section on inter-rater
reliability (5.3), and referenced this discussion in the threats to
validity (5.4) and the conclusion.  Furthermore, we expanded the discussion with statistical evidence that our IRR results were mostly
better than noise. We did extensive simulations sampling our ratings,
and then comparing those ratings against our ratings. We found that the
majority of our labels received higher IRR scores than 96\% to 99.9\%
of the random simulations. This allows us to confidently state that our
labels were primarily better than random. But we recognize that the
average of the values is low, and Section 5.3 address the threats this causes to
this paper, and what it might mean for practitioners and other
researchers when replicating this study. Section 5.3 also addresses the reviewers concerns that the IRR scores would
affect our ROC and F-Measure scores.
